Visualizations for the manuscript

### 2022-03-04 metanalysis_visualization/manuscript_Figures.Rmd
code added to get ITS per country. pvalue needs to be added

>>>>

Aggregated by Country

```{r}
patient_count_psy_period_psy_country <- patient_count_psy_period_psy_all %>% 
  left_join(country_map, by = "siteid") %>%
  group_by(country, time_p) %>% 
  mutate(total_patients = count_no_psy_patients +count_psy_patients) %>%
  summarise(psy_cases = sum(count_psy_patients),
            total_cases = sum(total_patients), 
            percentages = round(100*psy_cases/total_cases,2), 
            time = time, 
            period = period )

source( "time_series_analysis_plotting.R")
patient_count_psy_period_psy_country_france <- patient_count_psy_period_psy_country %>%
  filter( country == "France")
ts_linear_percent_france <- lm(percentages ~ period * time, patient_count_psy_period_psy_country_france)

time_series_analysis_plotting(ts_linear_percent_france,
                              patient_count_psy_period_psy_country_france,
                              "percentages",
                              clearance_period = FALSE) +
  labs(title = "Interrupted Time-Series Analysis: Percentage of encounters with psychiatric ICD codes (France)",
       subtitle = "Without seasonality effect",
       x = time_period,
       y = "Percentage")

patient_count_psy_period_psy_country_usa <- patient_count_psy_period_psy_country %>%
  filter( country == "USA")
ts_linear_percent_usa <- lm(percentages ~ period * time, patient_count_psy_period_psy_country_usa)

time_series_analysis_plotting(ts_linear_percent_usa,
                              patient_count_psy_period_psy_country_usa,
                              "percentages",
                              clearance_period = FALSE) +
  labs(title = "Interrupted Time-Series Analysis: Percentage of encounters with psychiatric ICD codes (USA)",
       subtitle = "Without seasonality effect",
       x = time_period,
       y = "Percentage")

```
```{r}
bootstrap_size <- 1000

binom_proportion <- function(n, prob, size) {
  (rbinom(n, size, prob) / size) * 100
}
bootstrapped_timepoints_france <- mapply(binom_proportion,
                                  n = bootstrap_size,
                                  size = patient_count_psy_period_psy_country_france$total_cases,
                                  prob = patient_count_psy_period_psy_country_france$percentages/100)
bootstrapped_sample_list <- vector(mode = "list", length = bootstrap_size)
bootstrapped_coefficients_list <- vector(mode = "list", length = bootstrap_size)
for (iteration in 1:bootstrap_size) {
  df_iteration <- data.frame(period = patient_count_psy_period_psy_country_france$period,
                             time = patient_count_psy_period_psy_country_france$time,
                             percentage = bootstrapped_timepoints_france[iteration, ])
  ts_linear_percent <- lm(percentage ~ period * time, df_iteration)
  linear_model <- broom::tidy(ts_linear_percent) %>%
    filter(term %in% c("time", "periodduring_pandemic:time"))
  coefficients <- linear_model$estimate
  names(coefficients) <- linear_model$term
  bootstrapped_coefficients_list[[iteration]] <- coefficients
  df_iteration$predicted <- predict(ts_linear_percent)
  df_iteration$time_p <- patient_count_psy_period_psy_country_france$time_p
  bootstrapped_sample_list[[iteration]] <- df_iteration
}
bootstrapped_fitted_df_france <- bind_rows(bootstrapped_sample_list, .id = "iteration")
bootstrapped_fitted_df_france$country <- "France"

bootstrapped_timepoints_usa <- mapply(binom_proportion,
                                  n = bootstrap_size,
                                  size = patient_count_psy_period_psy_country_usa$total_cases,
                                  prob = patient_count_psy_period_psy_country_usa$percentages/100)
bootstrapped_sample_list_usa <- vector(mode = "list", length = bootstrap_size)
bootstrapped_coefficients_list <- vector(mode = "list", length = bootstrap_size)
for (iteration in 1:bootstrap_size) {
  df_iteration <- data.frame(period = patient_count_psy_period_psy_country_usa$period,
                             time = patient_count_psy_period_psy_country_usa$time,
                             percentage = bootstrapped_timepoints_usa[iteration, ])
  ts_linear_percent <- lm(percentage ~ period * time, df_iteration)
  linear_model <- broom::tidy(ts_linear_percent) %>%
    filter(term %in% c("time", "periodduring_pandemic:time"))
  coefficients <- linear_model$estimate
  names(coefficients) <- linear_model$term
  bootstrapped_coefficients_list[[iteration]] <- coefficients
  df_iteration$predicted <- predict(ts_linear_percent)
  df_iteration$time_p <- patient_count_psy_period_psy_country_usa$time_p
  bootstrapped_sample_list_usa[[iteration]] <- df_iteration
}
bootstrapped_fitted_df_usa <- bind_rows(bootstrapped_sample_list_usa, .id = "iteration")
bootstrapped_fitted_df_usa$country <- "USA"

bootstrapped_fitted_all_by_country <- rbind( bootstrapped_fitted_df_france, bootstrapped_fitted_df_usa)

quantile_bootstrapped_fitted_country <- bootstrapped_fitted_all_by_country %>%
  group_by(time_p, period, country) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")

coefficient_slope_calculation <- function(df, ...) {
  ts_linear_percent <- lm(percentages ~ period * time, df)
  linear_model <- broom::tidy(ts_linear_percent) %>%
    filter(term %in% c("periodduring_pandemic:time"))
}

coefficients_df_by_country <- patient_count_psy_period_psy_country %>% 
  group_by(country) %>% 
  group_modify(coefficient_slope_calculation) %>% 
  rename(observed_diff = estimate)

df_coefficients_boot_by_country <- bootstrapped_fitted_all_by_country %>% 
  left_join(coefficients_df_by_country, by = "country")

names_countries <- unique(df_coefficients_boot_by_country$country)

plot_annotations_country <- df_coefficients_boot_by_country %>% 
  group_by(country) %>% 
  group_map( annotation_function ) %>% 
  set_names(names_countries) %>% 
  unlist()
plot_annotations_df_country <- data.frame(
  country = names(plot_annotations_country), 
  label_countr = plot_annotations_country
)

ggplot(bootstrapped_fitted_all_by_country, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("country", scales = "free_y") +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_country,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_country[quantile_bootstrapped_fitted_country$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_country,
             aes(y = percentages, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df_country, 
             aes(label=label_countr), 
            x = -Inf, y = +Inf, hjust=0, vjust=1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_country.png", height = 20, width = 32, units = "cm")
